Qualifying Examination Paper

### 2018-10-19 main.tex
181019-1611 sync

Wtihin the theme of semantic learning and generation, several significant contributions were made during 2016 and 2017.  Pathak, Krahenbuhl, Donahue, Darrell, and Efros successfully used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture was based on an encoder-decoder (TBD ref) combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The `reconstruction loss' is defined in terms of closesness ($L2$) of the filled area to the removed area. The encoder-decoder is regarded as $G$, and a new Discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$ was conditioned

>>>>

Wtihin the theme of semantic learning and generation, several significant contributions were made during 2016 and 2017.  Pathak, Krahenbuhl, Donahue, Darrell, and Efros used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture is based on an autoencoder \cite{hinton2006reducing} combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The `reconstruction loss' is defined in terms of distance ($L2$) from the filled area to the removed area. The encoder-decoder is regarded as $G$, and a new Discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$, but not $D$, was conditioned with context information \footnote{The paper defines context information as the missing pixels which, if true, undermines the objective (any statement of success should be based on withholding the missing pixels from the architecture).  I have requested clarification on this from the author (17 Oct 2018).}.

Luc, Couprie,Chintala and Verbeek applied a straightforward GAN approach to the task of semantic segmentation on images \cite{Luc2016SemanticSU}.  Their approach uses a Convolutional Neural Network (CNN) based generative model $G$ to learn a class label for each pixel in the image based on a ground-truth labeling (supervised), thereby creating a segmentation map of the input image.  The discriminative model $D$ takes a segmentation map and tries to classify it as being a ground truth map or a generated map.  While $D$'s objective function tries to maximize classification accuracy of the input segmentation map as being either ground truth or generated, $G$'s objective function tries to maximize pixel class labeling accuracy with respect to ground truth while also minimizing accuracy.

Reed et al. applied a GAN approach to the task of generating realistic images from text-based descriptions \cite{reed2016generative}.
